Scaling of Electrode-Electrolyte Interface Model Parameters In Phosphate Buffered Saline

### 2014-02-10 paper.tex
Added comment to reviewer

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    {\color{Red} Pull in more explination from JonathanScott2013 relating to the resistor mesh}
    No response yet.
}\\

@@

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    Item 12\\
    {\color{Red} ``shifts relatively little'' meaning at this impedance 50k is small compared to total resistance''}
    No response yet.
}\\

>>>>

page 2, in text/ table II. The scaling parameters and their meanings should be described more comprehensively. They remain somewhat unclear and meaningless to reader.\\
{\color{OliveGreen}
    Item 9\\
    We have encouraged the reader to review ScottSingle2013 in order to understand the interpretation of the given parameters. {\color{red} Should I just say they are resistances of elements in a resistor mesh?}
}\\

@@

page 2, line 52. "the magnitude shifts relatively little". However, In Fig. 4, logaritmic scale is used, and the change from 1.0X to 0.025X is almost 50k at the lowest frequencies. 
please clarify this point.\\
{\color{OliveGreen}
    Item 12\\
    Have reworded this slightly to convey that the shift in the CPE response is small relative to the shift in the resistance in the solution bulk. We are referring to a relative difference, a factor.
    {\color{red} I don't know how better to explain this, The difference between 9 000 000 and 1 000 000 000 is small compared to the difference between 20 and 2000}
}\\
